---
title: "Snapcount Timing"
author: David McGaughey
date: "2021-07-06"
output: html_notebook
---

# Load libraries
Tic toc is a lightweight timer
```{r}
library(snapcount)
library(tictoc)
library(tidyverse)
library(SummarizedExperiment)
```

# Pull data with snapcount / snaptron
One gene

About 2 seconds for GTEx and 3-10 seconds for SRAv3H
```{r}
tic()
sb <- QueryBuilder(compilation="gtex", regions=c("PAX6"))
pax6_gtex_gene <- query_gene(sb)
gtex_one_gene <- toc()

tic()
sb <- QueryBuilder(compilation="srav3h", regions="PAX6")
pax6_sra3h_gene <- query_gene(sb)
sra_one_gene <- toc()
```

## all in one 
```{r}
t_gene <- "PAX6"
sb <- QueryBuilder(compilation="srav3h", regions="PAX6")
pax6_sra3h_gene <- query_gene(sb)
meta <- read_tsv('SRP163355_meta.tsv')
colnames(meta) <- c('external_id', 'Condition')
snaptronId2GeneSym <- read_delim('../snaptron_id_to_gene_name.txt', delim = ':', col_names = c('snaptron_id', 'gene_name') )
counts <- assay(pax6_sra3h_gene) %>% 
  as.matrix() %>% 
  t() %>% 
  as_tibble(rownames = 'name') 
  match_column <- colnames(counts)[-1] %>% {filter(snaptronId2GeneSym, snaptron_id %in% ., gene_name == "PAX6")} %>% pull(snaptron_id)
counts_gene_meta <- counts %>% select(name, expression := as.symbol(!!match_column) ) %>% 
  left_join(colData(pax6_sra3h_gene) %>% as_tibble(rownames = 'name')) %>% 
  inner_join(meta) %>% 
  select(external_id, expression, Condition) %>% 
  mutate(gene_name = t_gene)
ggplot(counts_gene_meta, aes(x=Condition, y=log2(expression+1), fill = Condition)) +
                    #geom_point() + 
                    geom_boxplot() +
                    #scattermore::geom_scattermore(pointsize = 3, position = position_dodge(width = 1)) +
                    #geom_boxplot(width = 0.3)+
                    theme_cowplot() +
                    guides(x =  guide_axis(angle = 90)) +
                    scale_fill_manual(values = c(pals::brewer.set1(n=12), pals::brewer.set2(n=10)) %>% unname()) +
                    xlab('Gene') + facet_wrap(~gene_name, ncol = 5, scales = 'free_x')
  

```


```{r}
sb <- QueryBuilder(compilation="srav3h", regions="CRX")
pax6_sra3h_gene <- query_exon(sb)

snapcount::qu
```


# Pull in metadata from eyeIntegration
Has a bunch of tissue level ocular data
```{r}

```
# Make a "retina + GTEx" plot

## Extract data
```{r}
library(tidyverse)

tic()
gtex_data_build <- assay(pax6_gtex_gene) %>% 
  as.matrix() %>% 
  t() %>% 
  as_tibble(rownames = 'name') #%>% 
  # add in column data
  left_join(colData(pax6_gtex_gene) %>% as_tibble(rownames = 'name')) %>% 
  # label genes
  filter(Sample %in% meta$sample_accession) %>% 
  # join with meta
  left_join(meta, by = c('Sample' = 'sample_accession'))
gtex_data_toc <- toc()

tic()
#sra_data_build <- 

sra_data_toc <- toc()
```

## Plot
bit kludgy as I'm not certain how to grab the rowRanges info to get the `ENSG00000049449` version of Pax6
```{r}
tic()
bind_rows(gtex_data_build %>% mutate(Expression = `643`),
          sra_data_build %>% mutate(Expression = `8232`)) %>% 
  ggplot(aes(x=Tissue, y = log2(Expression + 1))) + 
    geom_boxplot() + 
  coord_flip() +
  theme_minimal()
ggplot_toc <- toc()
```

# Timings
THIS DOES NOT INCLUDE THE TIME IT TAKES TO DRAW THE GGPLOT IMAGE WHICH IS A FEW SECONDS
```{r}
tictoc_extract <- function(tictoc_data, name){
  time <- tictoc_data$toc - tictoc_data$tic
  time <- enframe(time) 
  time$name <- name
  time
}
timings <- bind_rows(tictoc_extract(gtex_one_gene, 'snapcount (GTEx)'),
          tictoc_extract(sra_one_gene, 'snapcount (SRA3H)'),
          tictoc_extract(gtex_data_toc, 'reformat GTEx data '),
          tictoc_extract(sra_data_toc, 'reformat SRA data'),
          tictoc_extract(ggplot_toc, 'ggplot2 call')) %>% 
  rename(value = 'Time') 

timings 

timings %>% 
  ggplot(aes(x=name,y=Time)) + 
  geom_bar(stat='identity') +
  coord_flip() +
  theme_minimal() +
  ylab('Time (seconds)') +
  xlab('')

```